\documentclass[12pt,oneside]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{geometry}

\setlength{\parindent}{0pt}
\titleformat{\chapter}[display]
  {\normalfont\bfseries\Large\centering}
  {\chaptertitlename\ \thechapter}{20pt}{\Large}

\newcommand{\dialogue}[3]{
	\begin{quote}
		\centering
		\vspace{0.25cm}
		\textit{#2} \\ \textbf{\footnotesize{#1}} \\\textit{\footnotesize{#3}}
		\vspace{0.25cm}		
	\end{quote}
}

\begin{document}

\pagestyle{empty}

\begin{titlepage}
	\centering
    \vspace*{\fill}
    {\Huge\bfseries Find It \\}
    \vspace*{\fill}
\end{titlepage}

The first time I asked about it, Coach was wrapping my hands.

The gym smelled like old leather and disinfectant. Heavy bags swung on their chains like lazy planets. I watched her work the tape between my fingers—quick, practiced—and the question slipped out before I had time to catch it.

\dialogue{The Fighter}{Coach… what’s the gauge?}{I asked}

\dialogue{Coach}{The gauge for what?}{She raised an eyebrow}

\dialogue{The Fighter}{For… whether I’m doing this right. Not just the fighting. Life. Work. All of it. Some philosopher probably has an answer, I assume.}{I hesitated}

\dialogue{Coach}{Philosophers usually have several. None of them pay gym rent.}{She smirked}

She finished the last wrap and pushed my gloves toward me, then leaned back on the old wooden stool like it was the throne of some tired, undefeated queen.

\dialogue{Coach}{All right. Here’s mine.}{...}

I braced myself.  
A Latin quote.  
A mountain metaphor.  
Something suitably mystical.

Instead, she said:

\dialogue{Coach}{You make a call. There are consequences. You take them. You learn. You move on. That’s the gauge.}{...}

\dialogue{The Fighter}{That’s… it?}{I stared}

\dialogue{Coach}{That’s as simple as it gets. You’re not judged by never making mistakes. You’re judged by whether you own what happens next.}{...}

I flexed my fingers inside the glove. The leather creaked, unconvinced.

She watched me for a second, then nodded toward the ring.

\dialogue{Coach}{Up. I think better when you’re getting punched.}{...}

We moved through a slow round. Jab–cross–breathe. Nothing fancy. Coach leaned on the ropes, calling out corrections like she was adjusting a machine she’d built years ago.

\dialogue{Coach}{Chin down. You’re not posing for LinkedIn. Again. Better.}{...}

Between combinations, she kept talking, like a tap had been opened.

\dialogue{Coach}{Find a way of living by your own code, and be willing to pay the price for it. That’s where it starts.}{...}

\dialogue{The Fighter}{My own code… like values?}{I asked, throwing another jab}

\dialogue{Coach}{Like rules you won’t break even when it hurts. That’s honor.}{...}

The word landed heavy. Heavier than the gloves.

\dialogue{Coach}{People dress it up. Speeches. Noble sacrifice. Big moments. But honor is simpler than that. You decide what kind of person you are, and you act like it when no one’s watching. Especially then.}{...}

I thought of late nights in front of a laptop.  
Of burying bugs under deadlines.  
Of blaming \textit{the system} when I knew exactly where I’d cut the corner.

\dialogue{Coach}{Find your honor. Because without honor, there’s no respect.}{...}

She stepped into the ring and tapped my glove down.

\dialogue{Coach}{Again. And listen—when I say respect, I don’t mean people liking your posts. I mean they can rely on you. They know you’re dangerous, but safe.}{...}

\dialogue{The Fighter}{Dangerous but safe? That sounds like a terrible dating profile.}{...}

\dialogue{Coach}{Best kind. You know how you earn it? Honor. Consistency. You say you’ll be there—you’re there. You say you’ll protect—you protect. You say you’ll own your mistakes—you own them.}{...}

I exhaled hard.

\dialogue{The Fighter}{And without respect, there’s no discipline}{I said quietly, remembering a line I’d scribbled in a notebook weeks earlier}

\dialogue{Coach}{Exactly. If you don’t respect yourself, why do the hard thing when you’re tired? Why get up at six to run, why learn, why grow? And if no one respects you, why care if you become a joke?}{She snapped her fingers}

She circled me slowly as I moved.

\dialogue{Coach}{Discipline is doing what you decided matters, even when you don’t feel like it. Honor tells you \textbf{what} matters. Respect is what keeps you from throwing it away when it’s inconvenient.}{...}

I let my guard drop, lost in the thought. She flicked my forehead with her glove.

\dialogue{Coach}{Hands up. Thinking’s good. Concussions, less so.}{...}

We sat on the edge of the ring for water, legs dangling.

\dialogue{Coach}{You’re restless again. Job stuff.}{...}

\dialogue{The Fighter}{They want to promote me. \textbf{Senior Software Engineer}. Sounds impressive. Part of me wants it. Part of me wants to run.}{I shrugged}

\dialogue{Coach}{Don’t marry the title. Not \textbf{Software Engineer}. Not \textbf{Senior}. Not \textbf{Supreme Archwizard of Microservices}.}{...}

I snorted into the bottle.

\dialogue{Coach}{Learn. Experiment. Break things. Fix them. Learn again. But don’t confuse the label with the life.}{...}

\dialogue{The Fighter}{So what am I supposed to say I am? At parties, I mean. People want a box.}{...}

\dialogue{Coach}{Try this: \textbf{I’m defining my own code of living.}}{She tilted her head}

\dialogue{The Fighter}{That sounds pretentious as hell.}{...}

\dialogue{Coach}{It is. Say it silently. Out loud, you can keep software. But in here}{she tapped my chest, gentle}

\dialogue{Coach}{Know the title is just packaging. What matters is whether you’re living by your code.}{...}

\dialogue{The Fighter}{And the price}{I added}

\dialogue{Coach}{And the price. Yes. You’ll disappoint people. You’ll say no. You’ll mess up trying to do the right thing and still hurt someone. That’s life—not a bug report.}{she said}

Her voice softened.

\dialogue{Coach}{You will be held accountable. Sometimes by others. Always by yourself. Your job isn’t to dodge that. It’s to honor it. To say: \textbf{I chose. This is on me. I’ll repair what I can, and I’ll carry what I can’t.}}{...}

We sat in the hum of the gym—distant thuds, the fan whining like it was tired too.

\dialogue{Coach}{Everyone needs a purpose. Man, woman, non-binary space wizard—I don’t care. It doesn’t have to be epic. It just has to be real. Something worth being disciplined for.}{she said}

\dialogue{The Fighter}{Like… fighting?}{I asked}

\dialogue{Coach}{Fighting’s just training. Same with coding. Same with parenting, composing, farming, running a food cart. Whatever you choose, you’ll have to learn to control your mind, your body, and your emotions if you want to be any good at it.}{...}

She leaned back on her hands.

\dialogue{Coach}{Only discipline gets you there. Motivation’s cute. Discipline is boring and holy.}{...}

\dialogue{The Fighter}{Holy?}{I echoed}

\dialogue{Coach}{In the sense that it keeps you aligned with what you say matters. That’s as sacred as it gets.}{...}

She glanced sideways at me.

\dialogue{Coach}{But here’s the twist. You don’t start with discipline. You start with respect. You treat yourself like someone whose life is worth not wasting. You treat others like they’re real—not NPCs. That grows into discipline. Live that long enough, and it becomes honor.}{she added}

\dialogue{The Fighter}{So it’s a loop. Honor, respect, discipline… back to honor.}{...}

\dialogue{Coach}{Careful. You’re doing philosophy.}{...}

We stayed after class. The gym emptied. Neon bled through the high windows. The city buzzed outside the cracked walls.

\dialogue{The Fighter}{I’m scared of choosing wrong. Of wasting my life on the wrong purpose. The wrong code.}{I admitted}

Coach nodded, like she’d heard it a thousand times.

\dialogue{Coach}{You will choose wrong. Several times. Congratulations—you’re alive.}{...}

\dialogue{The Fighter}{That helps}{I muttered}

\dialogue{Coach}{You’re not a statue picking a pose for eternity. You’re a creature in motion. You choose, there are consequences, you take them, you learn, you move on. That \textbf{is} the gauge. Not “was it perfect?” but “did I show up with honor, did I learn, did I try again better?”}{...}

\dialogue{The Fighter}{And if I don’t?}{I asked}

\dialogue{Coach}{Then you’ll feel it. In your gut. In the way you avoid mirrors. That’s your soul failing a unit test.}{she shrugged}

I laughed, despite myself.

\dialogue{Coach}{Stop waiting for permission. No title will make you valid. What you get instead is this: your own honor, your own respect, your own discipline. Yours to build. Yours to lose.}{...}

She turned serious, suddenly sharp.

\dialogue{Coach}{Find it. Not the one your parents wanted. Not the one your company posters sell. Not the one that performs well online. \textbf{Yours}. The one you’re willing to suffer for without becoming bitter.}{she said}

The gym felt smaller. Like we were sitting in the center of a much larger ring.

\dialogue{Coach}{And when you find it}{...}

she continued

\dialogue{Coach}{Protect it. Not with walls—with practice. With discipline. With how you treat people when you’re tired. With how you treat yourself when you’ve failed.}{...}

She slid off the ring, knees cracking.

\dialogue{Coach}{Story time’s over. Tomorrow. Same time. Bring your doubts—and your jab.}{said}

I watched her turn off the lights, one by one. The bags dissolved into shadow.

On the way home, my phone buzzed. Deadlines. Promotion talk. A recruiter offering a \textit{once-in-a-lifetime opportunity} identical to the last three.

I stared at the screen, then locked it.

No revelation. No trumpets. Just a quiet shift:
\begin{quote}
\textit{I didn’t know my full code yet. I didn’t know my grand purpose. But I knew this—I wanted to be someone I could respect. Someone who owned their choices. Someone who didn’t drop their gloves the second life hit back.}
\end{quote}

Maybe that was where honor began.

Under the streetlights, hands still aching under the tape, I whispered it like a promise. Like a small, serious spell:

\dialogue{The Fighter}{Find it.}{...}



\end{document}
