\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xparse}
\usepackage[utf8]{inputenc}

% ---------- Global script feel ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\raggedright

% ---------- Counters ----------
\newcounter{gnpage}
\newcounter{gnpanel}[gnpage]
\renewcommand{\thegnpage}{\arabic{gnpage}}
\renewcommand{\thegnpanel}{\arabic{gnpanel}}

% ---------- Tunable indents ----------
\newlength{\GNDialogueLeft}
\newlength{\GNDialogueRight}
\setlength{\GNDialogueLeft}{0.22\textwidth}
\setlength{\GNDialogueRight}{0.22\textwidth}

% ---------- Title block ----------
\NewDocumentCommand{\GNTitle}{ m m O{\today} }{%
  \thispagestyle{empty}
  \vspace*{0.18\textheight}
  {\Large\bfseries #1\par}
  \vspace{0.5em}
  {\large #2\par}
  \vspace{1em}
  {\itshape #3\par}
  \vfill
  \newpage
}

% ---------- Page ----------
% Usage: \begin{GNPage}[optional page subtitle] ... \end{GNPage}
\NewDocumentEnvironment{GNPage}{ O{} }{%
  \refstepcounter{gnpage}
  \setcounter{gnpanel}{0}
  \vspace{1em}
  {\bfseries PAGE \thegnpage%
    \IfValueT{#1}{ - #1}%
  }\par
  \vspace{0.5em}
}{%
  \vspace{1em}
}

% ---------- Scene / Environment ----------
\NewDocumentCommand{\Env}{ +m }{%
  {\bfseries\MakeUppercase{#1}}\par
}

% ---------- Panel ----------
% Starred version doesn't increment (useful for splash / non-numbered beats)
% Usage: \Panel[optional label]{description}
\NewDocumentCommand{\Panel}{ s O{} +m }{%
  \par\vspace{0.5em}
  \IfBooleanTF{#1}{%
    {\bfseries PANEL%
      \IfValueT{#2}{\ \textnormal{(\MakeUppercase{#2})}}%
    }\par
  }{%
    \refstepcounter{gnpanel}
    {\bfseries PANEL \thegnpanel%
      \IfValueT{#2}{\ \textnormal{(\MakeUppercase{#2})}}%
    }\par
  }%
  #3\par
}

% ---------- Action ----------
\NewDocumentCommand{\Action}{ +m }{%
  #1\par
}

% ---------- Caption / Narration ----------
\NewDocumentCommand{\Caption}{m m}{%
  {\itshape CAPTION (#1): #2}\par
}
\NewDocumentCommand{\Narration}{ +m }{%
  {\itshape NARRATION: #1}\par
}

\newcommand{\Aeluun}[2]{
\begin{center}
  {\textit{#1}} \\
  {\textit{\footnotesize{#2}}}
\end{center}
}

% ---------- SFX ----------
\NewDocumentCommand{\SFX}{ +m }{%
  {\bfseries SFX: \MakeUppercase{#1}}\par
}

% ---------- Transition ----------
\NewDocumentCommand{\Transition}{ +m }{%
  \hfill{\bfseries \MakeUppercase{#1}}\par
}

% ---------- Note to self (won't look like a panel element) ----------
\NewDocumentCommand{\Note}{ +m }{%
  {\small\itshape [NOTE: #1]}\par
}

% ---------- Dialogue ----------
% Usage: \Dialogue[optional parenthetical]{CHARACTER}{line(s)}
\NewDocumentCommand{\Dialogue}{ O{} m +m }{%
  {\par\noindent\centering\textsc{#2}\par}
  \begin{list}{}{%
    \setlength{\leftmargin}{\GNDialogueLeft}%
    \setlength{\rightmargin}{\GNDialogueRight}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\topsep}{2pt}%
  }%
    \item
      \IfValueT{#1}{\par}
      #3
  \end{list}%
}

% Optional quick beats
\NewDocumentCommand{\Beat}{}{%
  {\itshape (beat)}\par
}

\newcommand{\dedication}[1]{%
  \cleardoublepage
  \thispagestyle{empty}
  \vspace*{\fill}
  \begin{center}\textit{#1}\end{center}
  \vspace*{\fill}
  \cleardoublepage
}

\newcommand{\lyrics}[1]{%
  \begin{center}
  	\small (\scriptsize ( \tiny \textit{#1} \scriptsize )\small )
  \end{center}
}

\begin{document}

\GNTitle{KA\'{I}VEN | Chapter One: The End, The Beginning and The In Between}{noumena ashitaka hundim\"{a}gi-mei}[Draft \small{(v0.1)} - \today]

\dedication{
sa \\
helna varë \\
helna nü\\
sa elën\\
jää kai\\
silna na
}

\begin{GNPage}[THE MOUTH OF NIGHT]


\Panel[WIDE / EXTERIOR]{Wrecked ship suspended before a gargantuan black hole. The accretion disk burns like a fractured crown. Light bends, unwilling.}

\Caption{ZÁALI}{We have been running for so long that even the stars seem tired of witnessing it.}

\Caption{ZÁALI}{The ship is broken. Its bones cracked. Its skin torn. And there is no gentle harbor left in the void.}

\Panel[INTERIOR / BRIDGE WIDE]{Crew slumped at their stations. Consoles flicker and die. ZÁALI stands rigid, hands braced, as if holding reality together by force alone.}

\Caption{ZÁALI}{They trusted me. That trust is the sharpest thing in the room.}

\Panel[DETAILS / SYSTEM READOUT]{Cracked display: HULL 12\%. Structural failure imminent.}

\Caption{ZÁALI}{How many times can a man make the same choice and still call it courage?}

\Caption{ZÁALI}{How many times can he lead others into fire and insist it was \textbf{the only way}?}

\lyrics{caminos largos sin un final}

\Panel[CLOSE-UP / CREW FACES]{Silent tears. Trembling hands. Someone’s fingers hover near an eject lever, undecided.}

\Caption{ZÁALI}{Once, I wanted a simpler life.}

\Caption{ZÁALI}{A house. A door that locks. Mornings that mean bread, not battle.}

\Caption{ZÁALI}{But I stepped onto this road again and again, and each time I told myself it would be the last.}

\Panel[LOW ANGLE / ZÁALI + WINDOW]{The black hole swells, larger now, patient and absolute.}

\Caption{ZÁALI}{Why do I keep choosing this?}

\Caption{ZÁALI}{Why does it feel… like I am repeating myself?}

\Panel[FULL-BLEED / EXTERIOR]{The ship reduced to a speck, being pulled inward. Stars smear into wounded lines.}

\Caption{ZÁALI}{As if an unseen hand placed the pieces long before I ever reached the board.}

\Caption{ZÁALI}{As if the world has grooves worn deep into it, and my feet fall into them no matter how fiercely I resist.}

\Caption{ZÁALI}{If this ends the way it always ends… then what, in the name of every light that ever burned, was I meant to learn?}

\end{GNPage}

\begin{GNPage}[A SMALL GRAVE]

\Panel[WIDE / PARK]{A modest park. Trees. A bench. Summer light. At the edge, a small patch of freshly turned earth.}

\Caption{ZÁALI}{Pain is not a stranger. It is the oldest crewman aboard every ship I have ever flown.}

\Panel[MEDIUM / YOUNG ZÁALI]{ZÁALI, six years old, kneeling with a small shovel. Dirt stains his hands. His cheeks are wet. Beside him, a small bundle wrapped in cloth—his dog.}

\Caption{ZÁALI}{It sits quietly in the corner while we laugh, and it does not laugh with us.}

\lyrics{sabor a silencio en cada rincón, grita el vacío de mi corazón}

\Panel[DETAIL]{His small fingers press the earth down gently, carefully, as if tucking someone in for the night.}

\Caption{ZÁALI}{It watches us eat, and sleep, and make promises without knowing the price they will demand later.}

\Panel[MEDIUM / THE OLD MAN ENTERS]{A mysterious old man stands a few steps away. Simple clothes. Unremarkable. Yet somehow too still, as if the world has learned to pause around him. No menace. Only weight.}

\Caption{ZÁALI}{Then, when the alarms finally begin, it rises—quietly—as if it had been waiting all along for its true work.}

\Panel[TWO-SHOT / OLD MAN + CHILD]{The old man crouches to ZÁALI’s level. He keeps a respectful distance. Close enough to be present. Far enough not to intrude.}

\Dialogue{OLD MAN}{What was his name?}

\Panel[CLOSE-UP / YOUNG ZÁALI]{ZÁALI looks up. Eyes glassy. Throat locked. His mouth opens, but nothing comes.}

\Caption{ZÁALI}{They tell you existence is a gift.}

\Caption{ZÁALI}{If that is true, it is a gift wrapped in thorns—and the blood on the ribbon is usually your own.}

\Panel[MEDIUM / OLD MAN, SOFT]{The old man’s expression is calm. Tender. Certain in a way that is almost frightening, because it carries no doubt and no cruelty.}

\Dialogue{OLD MAN}{I know that hurt.

You will see them again...

Your dogs.

Just not the way you’re imagining right now.

Some things don’t come back the same way they leave.

You’re still too small to see the shape of it.

That’s all right.

Time has a way of explaining things without using words.}

\end{GNPage}


\begin{GNPage}[BACK TO THE SHIP]

\Panel[INTERIOR / BRIDGE]{A sudden jolt. Sparks burst from a console. The crew braces instinctively.}

\Caption{ZÁALI}{I have crossed a hundred skies. I have tasted a hundred triumphs.}

\Caption{ZÁALI}{None of them were clean.}

\Panel[EXTERIOR / SHIP]{The ship tumbles slightly as the gravity well tightens its pull.}

\Caption{ZÁALI}{Victory is just a word we use when grief has not caught up yet.}

\Panel[MONTAGE]{Fragments like broken memory: a helmet spinning slowly into darkness, a hand slipping away, a body wrapped and released into the void.}

\Caption{ZÁALI}{I remember faces the way sailors remember storms.}

\Caption{ZÁALI}{A smile that went out.}

\Caption{ZÁALI}{A hand reaching for mine… and finding nothing.}

\Panel[CLOSE-UP / ZÁALI’S HANDS]{His hands tremble. Then, deliberately, they steady.}

\Caption{ZÁALI}{I have buried companions in places that do not allow graves.}

\Caption{ZÁALI}{I have left them drifting where no planet will ever claim them.}

\Panel[CLOSE-UP / CREW MEMBER]{A crew member, awake now, stares at ZÁALI. The question is unspoken, but clear: why again?}

\Caption{ZÁALI}{It is a strange thing, to be called \textbf{leader}, when every step of your path is marked by those who followed you and did not return.}

\Panel[WINDOW / BLACK HOLE]{The black hole dominates the view now—immense, patient, inescapable.}

\Caption{ZÁALI}{Some nights, I wonder if I am a collector of endings.}

\Caption{ZÁALI}{And the worst of it is not that I lost them.}

\Caption{ZÁALI}{The worst of it is that I can still feel them… aching in the places they used to be.}

\end{GNPage}


\begin{GNPage}[THE OLD MAN LEAVES]

\Panel[MEDIUM / OLD MAN STANDS]{The old man rises. The effort looks practiced, almost performed, as if he is carefully remembering how an old body is supposed to behave.}

\Caption{ZÁALI}{There are losses you can accept—the swift, clean kind, where the universe is simply cruel and then moves on.}

\Panel[DETAIL / YOUNG ZÁALI’S FACE]{ZÁALI’s grief shifts. Confusion enters. Hope intrudes like an uninvited guest who does not ask permission.}

\Caption{ZÁALI}{And then there are the other losses… the ones that return.}

\Panel[WIDE / THE PARK PATH]{The old man begins walking away along the path. Sunlight gathers behind him, making distance feel intentional.}

\Dialogue{YOUNG ZÁALI}{…I’ll see him again?}

\Panel[OVER-SHOULDER / OLD MAN, NOT TURNING AROUND]{The old man does not look back—as if looking back would violate a rule he refuses to name.}

\Dialogue{OLD MAN}{Yes.}

\Panel[SURREAL HINT / CHILD POV]{For a fraction of a moment, the world slips: a bird freezes mid-motion, leaves hang too still, the old man’s outline \textbf{double-exposes}, as if time itself hesitated.}

\Caption{ZÁALI}{They do not return as they were.}

\Caption{ZÁALI}{A familiar laugh carried by a stranger’s mouth.}

\Caption{ZÁALI}{A gaze that once knew you, now sliding past as if you were smoke.}

\Panel[MEDIUM / YOUNG ZÁALI ALONE]{ZÁALI kneels by the small grave, watching the space where the old man was. The park feels larger now, as if it contains an infinite distance.}

\end{GNPage}

\begin{GNPage}[THE SEARCH BEGINS]

\Panel[MONTAGE / SPACEPORT CROWD]{Adult ZÁALI moves through a crowded spaceport on a distant world. He freezes—someone ahead carries a posture he knows too well.}

\Caption{ZÁALI}{I have found them again. Sometimes years later. Sometimes worlds apart.}

\Panel[MONTAGE / NEAR-MISS DOOR]{A door slides shut. ZÁALI arrives a moment too late.}

\Caption{ZÁALI}{…and I have missed them by a single choice, a single hour, a single wrong door.}

\Panel[MONTAGE / DIFFERENT LIFE]{A stranger laughs. The laugh is unmistakable—identical to someone we watched die—but the face is not theirs.}

\Caption{ZÁALI}{Do you know what it is to search for a person across the breadth of the cosmos, armed only with grief and intuition?}

\Panel[MONTAGE / SILHOUETTE]{A silhouette in rain and neon. ZÁALI’s breath catches, heart straining forward—then settling back. It is not them.}

\Caption{ZÁALI}{To see a shape in a crowd and feel your heart lunge like a dog at the end of its leash, only to be disappointed. Again.}

\Panel[MONTAGE / THE NAME FALLS]{ZÁALI speaks a name (speech balloon cropped). The stranger offers a polite smile. No recognition.}

\Caption{ZÁALI}{To speak a name you are no longer sure you have the right to speak, and watch it fall between you like something already dead.}

\Panel[BACK TO PRESENT / BRIDGE]{Adult ZÁALI stands on the bridge once more. His eyes are hollowed, shaped by years of searching.}

\Caption{ZÁALI}{They do not remember dying for me.}

\Caption{ZÁALI}{And I… I remember too much.}

\lyrics{en la sombra se esconden verdades... te busco en el aire en mil paisajes}

\end{GNPage}

\begin{GNPage}[THE ARCHITECT]

\Panel[SHIP SHUDDERS]{Reality leans, just enough to be noticed.}

\Caption{ZÁALI}{What finally breaks him is not the pain.}

\Caption{ZÁALI}{It is the pattern.}

\Panel[VISUAL PATTERN MONTAGE]{Fragments repeat across time: the same reaching hand, the same farewell, the same red warning light. As if the cosmos is working from a template.}

\Caption{ZÁALI}{The growing sense that suffering is not an accident, but a design.}

\Panel[BLACK HOLE AS EYE]{The black hole framed like an eye. For a heartbeat, the lensing suggests a face. Watching.}

\Caption{ZÁALI}{I have stared into the dark long enough to suspect it stares back.}

\Panel[THE “SEAM”]{A navigation map glitches into impossible geometry. For an instant, a faint grid appears behind the stars—then vanishes.}

\Caption{ZÁALI}{Some days, I can feel the seams of the world beneath my fingertips.}

\Panel[ZÁALI’S DECISION]{ZÁALI straightens. Not defiant. Resolved. The crew feels the shift without being told.}

\Caption{ZÁALI}{And I know… there will be another battle after this one.}

\Panel[HINT OF A GREATER WAR]{A symbolic panel: nine distant points of light, arranged with intention rather than chance. Or nine shadows implied in the lensing. Chosen.}

\Caption{ZÁALI}{Against the hands that set the rules of the game and call it existence.}

\lyrics{dime ¿dónde va lo que no se dice? ¿se pierde, se queda o cicatriza?}

\end{GNPage}


\begin{GNPage}[THE VOW]

\Panel[CREW QUIET]{A hand rests on a shoulder. Exhaustion shared. Intimacy without words.}

\Caption{ZÁALI}{If I were wise, I would let the dark take us gently.}

\Panel[TEMPTATION OF REST]{A peaceful composition—soft light, stillness—its edges poisoned by the pull of the black hole.}

\Caption{ZÁALI}{But I cannot.}

\Panel[FLASHBACK MICRO-BEAT]{A small, intrusive memory: young ZÁALI’s wet eyes. The old man’s voice, distant but intact.}

\Dialogue{OLD MAN}{You will see them again...}

\Panel[ZÁALI RISES]{ZÁALI straightens. Not louder. Sharper. As if something brittle has finally chosen to cut.}

\Caption{ZÁALI}{And if suffering is the law, then I will become its heresy.}

\Panel[FULL-BLEED / DOOR IN THE DARK]{Within the blackness: a hairline seam. A suggestion of a doorway, outlined by nothing at all.}

\vspace{3cm}
\center \textit{Lo var delna.}

\textit{Lo var na kaelle nor.}

\textit{Eth etheth silna varën, na eth kuul.} 

\textit{Ja na tal kaelna...}

\lyrics{cada sombra guarda un secreto pero mi sombra ya no tiene miedo}

\end{GNPage}

\end{document}
