\documentclass[12pt,oneside]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{geometry}

\setlength{\parindent}{0pt}
\titleformat{\chapter}[display]
  {\normalfont\bfseries\Large\centering}
  {\chaptertitlename\ \thechapter}{20pt}{\Large}

\newcommand{\dialogue}[3]{
	\begin{quote}
		\centering
		\vspace{0.25cm}
		\textit{#2} \\ \textbf{\footnotesize{#1}} \\\textit{\footnotesize{#3}}
		\vspace{0.25cm}		
	\end{quote}
}

\begin{document}

\begin{center}
  {\Huge\bfseries A Crack in the Stone}
\end{center}

\vspace{1.618cm}

I used to tell myself their words didn’t matter.  
That what people said about me—whispers, assumptions, quiet accusations—  
were nothing more than \textit{wind on stone}.  
Passing. Unfelt. Leaving no mark.

\vspace{0.618cm}

But that wasn’t entirely true.

\vspace{0.618cm}

The lies, the misunderstandings… those reached deeper.  
Not because they wounded me directly,  
but because they rendered me \textbf{unseen}.  
As if the version of me they assembled from fragments and shadows  
was more real to them  
than the truth I carried quietly, without defense.

\vspace{0.618cm}

For a while, I learned not to react.  
With each unspoken reply, I told myself I was winning—  
some private war of detachment.  
Perhaps I thought restraint was strength.  
Perhaps I believed silence made me impermeable.

\vspace{0.618cm}

Maybe that was what they wanted all along.  
A response.  
\textit{A crack in the stone}.

\vspace{0.618cm}

But what if it wasn’t manipulation?  
What if it was simpler than that—  
a hunger to be acknowledged?  
Perhaps, in my refusal to answer,  
they felt invisible too.

\vspace{0.618cm}

Strange, isn’t it?

\vspace{0.618cm}

We were both trying to be \textbf{seen}.

\vspace{0.618cm}

How can I blame them for that?

\vspace{0.618cm}

I could have spoken.  
I still could.  
But I’ve learned that not everything asks for a voice.  
Some truths settle better in stillness,  
carried not by words,  
but by understanding.

And sometimes,  
\textit{silence is the loudest reply}.


\end{document}