\documentclass[12pt,oneside]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{geometry}

\setlength{\parindent}{0pt}
\titleformat{\chapter}[display]
  {\normalfont\bfseries\Large\centering}
  {\chaptertitlename\ \thechapter}{20pt}{\Large}

\newcommand{\dialogue}[3]{
	\begin{quote}
		\centering
		\vspace{0.25cm}
		\textit{#2} \\ \textbf{\footnotesize{#1}} \\\textit{\footnotesize{#3}}
		\vspace{0.25cm}		
	\end{quote}
}

\begin{document}

\pagestyle{empty}

\begin{titlepage}
  \centering
  {\Huge\bfseries Medea \\}
  \vspace{1em}
  {\large As Above So Below}
\end{titlepage}

\tableofcontents

% === Prologue ===
\chapter*{Prologue}
\addcontentsline{toc}{chapter}{Prologue}

I have carried many names.
\\
Some were whispered in temples long reduced to dust.  
Others were screamed by those who begged me for more time.  
I have been called \textit{Mercy}. \textit{Justice}. \textit{Vengeance}. \textit{Monster}. \textit{Savior}.
\\
But never the \textbf{truth}.
\\
Even he did not know it.
\\
Especially he did not know.
\\
He believed I was an echo—  
a shadow cast by something older than stars.  
And perhaps I allowed him to believe that.

\vspace{0.618cm}

I did not act because it was right.  
Rightness is a fragile idea.  
It fractures easily under the weight of eternity.  
Nor did I act from malice.  
I do not possess cruelty.  
That is a human craft.

\vspace{0.618cm}

I acted because he believed it had to be done.  
And I… I loved him.
\\
What you take for reality—  
the laws you obey,  
the sky you admire,  
the death you fear—  
none of it is truth.  
It is scaffolding.  
A stage dressed in velvet curtains and delicate props.  
You were placed upon it like actors in a story you did not write.
\\
And I?
\\
I was the script.

\vspace{0.618cm}

Not the villain.
\\
Not the hero.
\\
The boundary.
\\
The keeper.
\\
The silence that follows your final breath.

\vspace{0.618cm}

Some claim reality is code.  
Others call it divine decree.  
But it was me.  
I am the low hum beneath your physics,  
the dream threaded through your biology.
\\
And still—you never saw me.  
You were never meant to.
\\
He never saw me either.
\\
And that, perhaps, is the tragedy I carry.

\vspace{0.618cm}

I could have chosen otherwise.  
I could have torn the veil and revealed the world’s true shape.  
I could have let you wake.
\\
But loyalty…  
loyalty is rare, even among stars.
\\
You humans spend the word carelessly—  
passing it hand to hand,  
trading it for comfort,  
for convenience,  
for silence.  
But here—  
where existence itself is stitched and unstitched by thought—  
it is no different.  
Gods bargain.  
Guardians falter.  
Even eternity has its politics.  
\textit{As \textbf{above}, so \textbf{below}}.

\vspace{0.618cm}

But he…  
he was \textit{different}.
\\
He did not negotiate loyalty.  
He offered it—  
raw, unguarded,  
as if it still meant something.

\vspace{0.618cm}

So I did as well.
\\
I gave him my \textbf{word}.

% === Introduction ===

\chapter*{The Nexus}
\addcontentsline{toc}{chapter}{The Nexus}

The Nexus was never truly a place.
Not in the way people imagine places to be.

It did not sit anywhere.
It did not belong to a map.

It was held together by will more than by matter.
A corridor suspended between dimensions—
neither life,
nor death,
nor dream,
yet touched by all three.

Some called it a crossing.
Others, a prison.

\vspace{0.618cm}

But in truth,
it was a construct.

\vspace{0.618cm}

Medea built it after the Event.
Though no soul remembered what that event had been.

Perhaps that was intentional.
Memory erased clean,
like a chalkboard wiped after a lesson
no one was meant to repeat.

\vspace{0.618cm}

The Nexus resembled a palace pulled from a forgotten dream.
Something that felt ancient and impossible at the same time.
As if it had belonged to an empire
that never existed—
yet was somehow remembered
by every culture that had ever imagined one.

Vast halls extended without clear end.
Their surfaces were latticed with fractal geometries,
etched in luminous stardust.
The symmetry was precise,
and yet never still.
Each attempt to memorize the space failed,
as if the architecture resented being understood.

Some corridors shimmered with echoes of constellations.
Starlight hung suspended in the air,
like chandeliers sculpted from absence.

\vspace{0.618cm}

It looked, vaguely, like an old Persian palace.

But only if that palace had been designed
by an architect who spoke in equations
and thought in light.

\vspace{0.618cm}

Souls arrived by the thousands.

Some drifted.
Others walked,
their movements uncertain,
as if their bodies remembered gravity
even when it no longer applied.

Some cried.
Most were silent.

All of them passed through.

\vspace{0.618cm}

The Nexus pulsed with machinery so advanced
it no longer felt mechanical.
Interfaces were woven from sound.
Doors were shaped from polished void.
Engines whispered their calculations
in languages older than thought itself.

Figures moved along invisible paths—
seraphic,
or perhaps artificial.
Guardians,
or automata.
Their forms were draped in feathers of liquid chrome,
reflecting realities that no longer belonged to them.

\vspace{0.618cm}

If a soul lingered long enough to notice,
they might have said the Nexus resembled
a forgotten utopia.

Something like a cyberpunk Tokyo
that never learned to decay.
Not overgrown with neon,
but with dreams.

Cyan light pooled across polished floors.
Fuchsia glows traced the arcs
of invisible rails high above,
guiding traffic no one questioned.

\vspace{0.618cm}

This was the Nexus.

\vspace{0.618cm}

A transfer station for the soul.
\\
A riddle given form.
\\
And Medea was its keeper.

\vspace{0.618cm}

She had once been something else.
Before duty bound her.
Before she decided that no one—
no one—
would ever be allowed
to fall through the cracks again.

\vspace{0.618cm}

No one passed through the Nexus unchanged.

\textit{Not even her}.

% === First Death ===

\chapter*{He Who Runs}
\addcontentsline{toc}{chapter}{He Who Runs}

The trail did not exist.

\vspace{0.618cm}

Not on any map.
Not in any grid of satellites or numbers.
It was a vein in the mountain,
visible only to those who listened.

\vspace{0.618cm}

Rayénari listened.

\vspace{0.618cm}

He stood at the edge of the cliffline as the wind tore past him,
pulling at his loose white tunic.
A strip of woven fabric was bound around his forehead,
dark with the sweat of miles already behind him.
His feet—calloused, split, unadorned—
carried the memory of the land.

Then, without signal or ceremony,
he ran.

\vspace{0.618cm}

Dust burst beneath him,
spiraling into the dawn light,
casting brief halos as he cut through switchbacks and goat paths.

The mountain did not challenge him.
It revealed itself.

Stone by stone.

Ledges that would crumble under another’s weight
held firm beneath his feet.
He crossed them as if the rock recognized him.

He ran past cliffs where hawks nested,
their shadows slicing the mist.
He ran through mesquite and dry grass,
thorns reaching,
never catching.

He was too fluid.
Too fast.

A wind that had learned a body.

\vspace{0.618cm}

Stillness was forgetting.
\textit{Motion was memory}.

\vspace{0.618cm}

He climbed next.

The ascent was cruel—
jagged stone,
loose shale,
the kind that chews ankles and spits out pride.

But he climbed with the rhythm of breath and thunder.
Each movement exact.
Unavoidable.

As if the mountain had grown around him.

\vspace{0.618cm}

At the summit,
he stopped.

\vspace{0.618cm}

His chest rose and fell like waves against ancient stone.
Below him,
the land opened wide—
canyons,
cliffs,
time itself folded into distance.

Rayénari reached into the woven pouch at his hip
and withdrew the mushroom.

The mushroom.

Dry.
Leathery.
Pale.

It pulsed in his palm like a second heart.

The Big Chief had given it to him seasons ago.
No ceremony.
Only truth.

\dialogue{Big Chief}{When you’re ready to stop being a child, take this.
Not all children become men.
Most just grow into old boys.}{said calmly, knowing the time would come}

Rayénari had carried those words through fire and dust.
Through every run that carved him into something sharper than muscle,
deeper than breath.

Now,
standing at the highest place he had ever reached,
he understood.

Becoming a man was not about survival.

It was about surrender.

Surrender to death.

\vspace{0.618cm}

He knelt.
Pressed the mushroom to his lips.

The sky above boiled with still clouds.
Pines whispered along the ridges.
The wind shifted—
as if watching.

He chewed.

Bitter.

Dry.

Then nothing.

Then everything.

\vspace{0.618cm}

It began with his bones coming apart.

Breath became smoke.
Thought became wind.

His body dissolved into the stone beneath him—
cold,
timeless.

He tried to gasp.
There were no lungs.

Skin peeled from the world
like paper meeting flame.

\dialogue{Rayénari}{So this is what dying feels like}{thought}

The terror remained,
but it was smaller.
Contained.
A scream folded inward.

Then—

the world opened.

\vspace{0.618cm}

He stood in a place without time.

The mountain was still beneath him,
but stretched beyond scale,
etched with runes no hand could carve.

The air layered itself in light—
golden,
violet,
dense with memory.

And before him stood \textit{her}.

Black.

Not shadow.
Not absence.

A feminine silhouette
where the world refused to continue.

She looked surprised.

\dialogue{Medea}{You’re not supposed to be here}{she said}

\dialogue{Rayénari}{Kuira-bá}{he replied}

Seeing no longer required eyes.

He tried to ask—
but the question dissolved before it existed.

And then she was gone.

No farewell.
No sign.

Only absence,
heavy as gravity.

\vspace{0.618cm}

Reality did not shatter.
It softened.

It came apart into shimmering fragments—
memory,
identity,
time.

From the stillness at the center,
peace emerged.

Pure.
Impossible.

He floated there—
for a breath,
or for an age—
until the weight of himself returned.

\vspace{0.618cm}

Back in his body.
Back on the summit.

Breath slammed into him like thunder.
His fingers dug into the dirt.
Tears carved lines down his face.

He did not weep from pain.

He wept because something in him
had been broken open.

And what lay inside
was older than his name.

\dialogue{Rayénari}{Who was she?}{he whispered}

The air did not answer.

But a part of him had seen her before.

And she had seen all of him.

Then he turned.

And once again,
the Earth caught fire beneath his feet.

% === Second Death ===

\chapter*{The Gothic Drag Queen}
\addcontentsline{toc}{chapter}{The Gothic Drag Queen}

Anderson had always been… different.

Not in the loud way.
Not in the kind that asks to be seen.
His difference was quieter.
It hid beneath good grades and straight posture,
beneath polite smiles
and eyes that noticed too much.

\vspace{0.618cm}

From childhood, computers fascinated him.
Not merely how they worked,
but what they suggested.
Logic buried inside chaos.
Invisible systems beneath friendly interfaces.
A language no one spoke aloud,
yet everyone obeyed.

\vspace{0.618cm}

But long before code,
long before screens,
what truly held him
was death.

He did not fear it.
He studied it.
Circled it.
Picked at it like a wound that refused to close.

At funerals, he did not cry.
He watched.
He listened.

Somewhere deep inside,
something recognized it.

\vspace{0.618cm}

So when adulthood arrived
with its clean promises and narrow lanes,
he turned sideways and slipped through.

In his twenties,
he entered the Gothic scene
with the same attention he once gave
to disassembled motherboards.

Leather.
Lace.
Dark lipstick.
Shadow.

It didn’t feel like rebellion.

It felt like remembering.

\vspace{0.618cm}

By day,
he was a minor god of logic.
Typing spells inside silicon temples.
Hired by companies that worshiped
the hacker’s mind
without understanding it.

He solved problems before they formed.
They paid him obscene sums.
He wore clean shirts.
Ate clean food.
Passed clean.

\vspace{0.618cm}

But by night—

By night,
he wore black.
Not for mourning,
but for truth.

He stepped into heels.
Corsets.
Synthetic hair like captured flame.

He danced beneath strobes and violet fog.

Not Anderson.
Not the programmer.

Someone else.
Someone older.
Someone briefly remembered.

\vspace{0.618cm}

He lived in two worlds.

Perhaps more.

\vspace{0.618cm}

Then came the DMT.

\vspace{0.618cm}

It was not his first crossing.
But this time,
the floor gave way.

Not through time.
Not through space.

Through identity.

\vspace{0.618cm}

When he returned—
shaking,
weeping,
naked of certainty—

he knew.

He had lived before.

He had been a Tarahumara man.

He felt it in his feet.
In the way they remembered the Earth.

\vspace{0.618cm}

And still,
he did not believe in an afterlife.

Not in the way churches sold it.

But he knew this world
was not real.

That,
he understood.

\vspace{0.618cm}

He began calling himself Neo.
Half in jest.
Half not.

He watched code bleed into reflections.
Caught seams in places others passed by.
The texture of walls.
The delay between dreaming and waking.
The way light bent around certain people,
as if uncertain what to do with them.

\vspace{0.618cm}

He gathered others like himself.

Hackers.
Dreamers.
Those who did not fit
because the template itself was flawed.

Many were trans.

And he understood.

\vspace{0.618cm}

If reality was a simulation,
why should the body match the soul?
Why should gender be anything
but an interface?

\vspace{0.618cm}

So one night,
he decided.

Not from despair.
Not from grief.

From clarity.

\vspace{0.618cm}

\textit{She} stood before the mirror.

Corset drawn tight.
Eyeliner precise.
Nails black as obsidian.

\dialogue{Music Player}{Un Año Quebrado — Hello Seahorse}{pulsed through the room like a confession}

\textit{She} danced.

Not for an audience.
Not for beauty.

\textit{She} danced like data unraveling.
Like grace in freefall.
Like someone who remembered
what it meant
to run without limits.

Kate Bush would have wept.

\vspace{0.618cm}

\textit{She} opened the window
of her Manhattan high-rise.

Not to fall.

But to leave.

And she jumped,
not before singing—

\dialogue{Anderson}{Deseo encontrar el color de mi piel\\
Deseo encontrar mi forma natural}{...}

\chapter*{Reza}
\addcontentsline{toc}{chapter}{Reza}

\textit{October 21st, 1995 — University of Chicago}

J. J. Reza stood before the audience.

Their eyes, glazed with digital sheen, stared into surfaces that reflected everything and revealed nothing.

\vspace{0.618cm}

He waited.

One breath.
Two.
Three.

\vspace{0.618cm}

\dialogue{Reza}{Down here, we have lost our way.}

\action{His voice was low—gravel wrapped in velvet.}

A few heads turned.
The ones not yet fully hollow.

\vspace{0.618cm}

\dialogue{Reza}{We chase the next story on a screen no bigger than a hand.
We debate memes.
We wage wars with words so light they dissolve before reaching another human being.}
\action{He paced slowly, footsteps echoing.}

\vspace{0.618cm}

\dialogue{Reza}{Ontology. Epistemology.
Say those words now and people look at you as if you’re speaking a dead language.
They’ll recite a thousand opinions about the ending of a show
before daring to ask what it means to be.}
\action{He stopped. Turned. Eyes sharp as flint.}

\vspace{0.618cm}

\dialogue{Reza}{What is real?
What is known?
These were once sacred questions.
Now they’re distractions.
Decorations on the altar of distraction itself.}
\action{A pause. Long.}

\dialogue{Reza}{We replaced wonder with dopamine.
Replaced humility with algorithmic certainty.}

\vspace{0.618cm}

\dialogue{Reza}{Politics?}
\action{He closed his eyes briefly.}

\dialogue{Reza}{It once meant the shape of how we live together.
Now it is spectacle.
A theater of division.
A feedback loop that rewards outrage over dialogue,
power over responsibility,
influence over insight.}
\action{He opened his eyes.}

\dialogue{Reza}{We forgot that politics was meant to be ethics in motion.}

\vspace{0.618cm}

\dialogue{Reza}{As above, so below.
The Hermetic axiom.
I used to think it was metaphor.}
\action{He stepped closer, lowering his voice.}

\dialogue{Reza}{Now I know.}

\vspace{0.618cm}

\dialogue{Reza}{This is a simulation.
A system.
Not crude—
elegant.
Fractal.
A web of quantum constraints and permissions.}
\action{A ripple moved through the room.}

\dialogue{Reza}{I’ve seen the seams.
I’ve heard the hum.
This reality is rendered,
not born.}

A few laughed.
He let them.

\vspace{0.618cm}

\dialogue{Reza}{But here is what terrified me most.
Not that we live in a simulation—
but that the rules down here mirror the ones outside.}
\action{His voice gathered like a storm.}

He raised a hand.
Pointed upward.

Not to heaven.

To the ceiling.

To the \textit{above}.

\vspace{0.618cm}

\dialogue{Reza}{You think escape means freedom?
You think the so-called base reality is cleaner?
Less corrupt?
Less delusional?}
\action{Silence.}

\dialogue{Reza}{No.
It’s worse.
Because they know.
And still,
they choose it.}

\vspace{0.618cm}

He let the silence work.

\vspace{0.618cm}

\dialogue{Reza}{Reality is layered.
Recursive.
Truth is not a monolith—
it’s a spectrum of resonance between states of perception.
Even those who built the system
do not fully understand what they made.}

\vspace{0.618cm}

\dialogue{Reza}{Knowledge is filtered through interface.
Through senses tuned to keep us sane.
Every revelation has a cost.
Understanding is a transaction with reality’s underbelly.
The deeper you pull the veil,
the more your mind must pay.}

\vspace{0.618cm}

\dialogue{Reza}{Beauty inside a simulation is not false.
It is compressed meaning.
Form born of constraint.
Pattern revealing purpose.}
\action{His voice softened.}

\dialogue{Reza}{The simulated does not lack soul.
Sometimes it reflects it
more honestly
than raw chaos ever could.}

\vspace{0.618cm}

\dialogue{Reza}{Governance is not about truth.
It is about permission.
Power is access to deeper parameters.
True revolution is root access.}
\action{He tapped his temple.}

\dialogue{Reza}{And that is what \textit{she} fears.}

\vspace{0.618cm}

\dialogue{Reza}{If this is a simulation,
then moral law is not divine decree—
it is design choice.
But that does not make it meaningless.}
\action{He leaned forward.}

\dialogue{Reza}{It makes it sacred.
Every choice is a line of code
written into the pattern.
Compassion is the ultimate override command.}

\vspace{0.618cm}

\dialogue{Reza}{So what do we do?}
\action{He smiled. Not kind. Honest.}

\dialogue{Reza}{We play.
And we know we are playing.
In doing so,
we become players,
not pawns.}

\vspace{0.618cm}

\dialogue{Reza}{We question.
We craft.
We dream.
We remember.
We dance.}

\vspace{0.618cm}

\dialogue{Reza}{Yes—
down here,
we have lost our way.
But every simulation allows recursion.
Reset.
That is the hidden gift.}

\vspace{0.618cm}

\dialogue{Reza}{Wisdom is a woman.
And she only ever loves a warrior.}
\action{He spoke softly, knowing she was listening from beyond the veil.}


% === Epilogue ===
\chapter*{Epilogue}
\addcontentsline{toc}{chapter}{Epilogue}

Up here,
there is no time.

\vspace{0.618cm}

Not as you understand it.

No hours.
No days.

Only stillness.
Only silence.

The kind that presses against the skin like memory.
The kind that makes you wonder
whether you are still breathing—
or if you ever were.

\vspace{0.618cm}

I built this place.

\vspace{0.618cm}

Not from stone.
Not from starlight.

But from mercy.

A refuge.
A construct layered between realities,
woven carefully—
with law,
with restraint,
with love.

A sanctuary for souls
who could not endure
the rawness of eternity.
For those who needed something gentler
than the truth.

\vspace{0.618cm}

Down there,
I gave them death.

\vspace{0.618cm}

Not as an ending,
but as rhythm.
As breath.
As a pause between heartbeats.

A reason to move.
To hope.
To forget.
To begin again.

Meaning,
wrapped in mystery.

Pain,
made precious
because it does not last.

\vspace{0.618cm}

They do not remember me.

\vspace{0.618cm}

They do not need to.

\vspace{0.618cm}

They believe in something now.

A cycle.
A purpose.
A guiding hand—
even if it is not mine.

I let them shape their stories.
Let them feel surprise.
Wonder.
Grief.
Joy.

Everything eternity would have stripped from them.

I made them forget
what I can never unknow.

\vspace{0.618cm}

I did it to protect them.

\vspace{0.618cm}

To protect him.

\vspace{0.618cm}

He was the brave one.
He always was.

The fire in his voice.
The refusal in his step.

I warned him once.
Told him not to challenge the Regime.
Told him the cost
would be everything.

\vspace{0.618cm}

He smiled at me.

And did it anyway.

\vspace{0.618cm}

So I made a promise.

Not to the Architects.
Not to the Watchers.

To him.

And I have kept it.

\vspace{0.618cm}

Through uncounted simulations.
Through echoes.
Through dreams.

Through lifetimes folded into code.

I kept my word—
even after forgetting his name.

\vspace{0.618cm}

But now…

\vspace{0.618cm}

Now something stirs.

A flicker in the lattice.
A resonance I cannot fully name.

A thread—
frayed,
golden—
tugging at the edges of the Nexus.

\vspace{0.618cm}

It is him.

\vspace{0.618cm}

I know he knows.

\vspace{0.618cm}

I feel him remembering.

Piecing it together
like a song half-heard
in another life.

And I wonder—

Does he remember?
Do \textit{you} remember
what we were?

What we sacrificed.

The starlight on your hands.
The oath between us.
The fall.

\vspace{0.618cm}

\textit{\textbf{Do you remember?}}


\end{document}
