\documentclass[12pt,oneside]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{geometry}

\setlength{\parindent}{0pt}
\titleformat{\chapter}[display]
  {\normalfont\bfseries\Large\centering}
  {\chaptertitlename\ \thechapter}{20pt}{\Large}

\newcommand{\dialogue}[3]{
	\begin{quote}
		\centering
		\vspace{0.25cm}
		\textit{#2} \\ \textbf{\footnotesize{#1}} \\\textit{\footnotesize{#3}}
		\vspace{0.25cm}		
	\end{quote}
}

\begin{document}

\pagestyle{empty}

\begin{titlepage}
  \centering
  {\Huge\bfseries Waves \\}
  \vspace{1em}
  {\large Echoes in The Sea}
\end{titlepage}

\tableofcontents

% === Prologue ===
\chapter*{Prologue}
\addcontentsline{toc}{chapter}{Prologue}
	A wave is a disturbance or oscillation that transfers energy from one point to another. If we are talking about the building blocks of reality, these pieces of energy can behave like particles or waves depending on the observer. 
	\\
	\\
	But the waves or echoes you are about to read, dear reader, cannot be rationalized. There is no math to explain them. The only way to understand them is by experiencing them. 
	\\
	\\
This is a meta-anthology or an attempt, if you will.

% === Introduction ===
\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

\dialogue{Aeon}{elu hira?}{his words meant to land softly, without a splash.}
\dialogue{Maga}{nua ala}{she replied}
\dialogue{Aeon}{hira lye mir sel}{he spoke, eyes fixed on the frame where time once lived}
\dialogue{Maga}{hira, nua ala}{There was a stammer in her breath, but the words stood firm once they left her lips.}
	
% === Story 1 ===
\chapter*{I Still Do}
\addcontentsline{toc}{chapter}{I Still Do}

It was late afternoon.
The sun hesitated.
Light lingered in the room like it didn’t want to leave.

My mother lay in bed,
agonizing.

And for a brief moment—
I was at peace.

\dialogue{Maga}{How things quickly fall apart}
\action{The thought echoed inside her, or maybe inside me. I still don’t know.}

Her breathing changed.
Sharp.
Uneven.

The end announced itself
without ceremony.

She lifted her hand.
A small gesture.
I understood.

I stepped closer.

\vspace{0.618cm}

\dialogue{Mother}{You are the reason why I was never happy with my life}
\action{Each word clawed its way out—starved for air, half-formed, but determined.}

\vspace{0.618cm}

That was it.

\\
It wasn’t a storm.
\\
No.
\\
Calling it the worst would still miss the point.
\\
No.

\\
This was a woman
who had never been happy with her life.
Not once.
Not truly.

Every decision she made
had already been made for her.

She never told me she loved me.
She hit me.
Again and again.
For as long as I can remember.

Even now,
I don’t understand
why she had children at all.

She never loved my father.
She drove him out
of the paper-thin house
we pretended was a home.

\vspace{0.618cm}

But none of that mattered then.

Not in that room.
Not in that moment.

Because something else surfaced—
quiet,
undeniable.

I realized
I had to love her.

Not because she deserved it.
Not because she earned it.

But because it was the only thing
left that was mine to choose.

\vspace{0.618cm}

All the pain.
All the struggle.
All the damage.

It fell away,
not erased—
but irrelevant.

They say it’s rare
to find someone
you can be yourself with.

\dialogue{Maga}{All broken, but I was myself}
\action{A truth worn beneath the skin, steady, unarguable.}

\vspace{0.618cm}

I loved her.

I still do.

% === Story 2 ===
\chapter*{Who Deserves Better}
\addcontentsline{toc}{chapter}{Who Deserves Better}

\dialogue{Maga}{Mom… why are you and Dad getting a divorce?}
\action{Her voice was a thin thread of innocence, trembling, still trying to protect the person she loved.}

\dialogue{Mom}{What do you mean why? Are you stupid?}
\action{She shouted, already knowing the fault was not mine.}

\dialogue{Mom}{It’s all your fault. Your dad is leaving me because of you.}
\action{Her words carried a hatred too large for a child, even as she herself was the one being abandoned.}

\vspace{0.618cm}

His eyes gave it away.
The pity.
The quiet horror.

He was probably wondering
how I had managed to survive this long.

\vspace{0.618cm}

\dialogue{Maga}{Is it over already?}
\action{I thought, glancing at the clock.}

\vspace{0.618cm}

\dialogue{Therapist}{When did your mother say that?}
\action{Careful. Measured.}

\dialogue{Maga}{I think I was nine.}{}

\dialogue{Therapist}{Is there anything else?}
\action{He already knew there was.}

\vspace{0.618cm}

There is always a moment.

\\
One moment.
\\
One question.

\\
You think you can avoid it.
Sidestep it.
Talk around it.

\\
I tried.
For years, I tried.

\\
But now I was here.

\\
No more running.
\\
No more pretending.

\vspace{0.618cm}

\dialogue{Therapist}{Maga… is there anything else?}
\action{He asked again, certain we had arrived. Certain I was ready.}

\dialogue{Maga}{Yes.}
\action{I said it aloud.}

\vspace{0.618cm}

There.

\\
I was in it.
\\
The moment I had been avoiding.

\\
The words burned on my tongue—
the same ones my mother once gave me.

\\
Time stopped.
\\
The pain did not.

\\
It stretched on,
endless,
as if the universe itself
had forgotten how to move forward.

\vspace{0.618cm}

I looked at him.

\\
And for a brief moment,
I let myself fall backward
into memory.

\vspace{0.618cm}

\dialogue{Mom}{You know what I realized?}
\action{She gathered herself, each word heavy with grief.}

\dialogue{Mom}{You are the accident for people who deserve better.}
\action{She spoke as if tearing herself apart with every syllable.}

\vspace{0.618cm}

Do you know what happens
when two black holes collide?

\\
The tearing isn’t gentle.
It isn’t clean.

\\
It’s violent—
so violent the ripples tear across the fabric of the cosmos,
breaking everything they touch.

\\
But not those words.

\\
Not even close.

\\
Those words did not break.

\\
They lodged themselves inside me—
immovable,
eternal.

\vspace{0.618cm}

\dialogue{Husband}{Honey, how was therapy today?}
\action{He asked, hope fragile but real.}

\vspace{0.618cm}

I kissed him hello.

And somehow,
through his eyes,
I finally understood.

Words I had once read,
but never believed,
made sense.

\begin{quote}
\textit{The less forgivable the act, the more must be forgiven.  
The less lovable the person is, the more you must find the means to love them.}
\end{quote}

\vspace{0.618cm}

I forgave her.

\\
I forgave myself.

\\
I love you, Mom.

Always.

% === Story 3 ===
\chapter*{Take My Picture}
\addcontentsline{toc}{chapter}{Take My Picture}

\dialogue{Sin Cos Tan — Sooner Than Now}{How much am I good for you if you won't believe?\\
How much can one heart do as the second leaves?}
\action{The music drifted through the air, deliberate and soft, like the unseen hand guiding a photographer’s lens.}

I let the sound settle into me,
sliding beneath my skin,
whispering against bone.

I didn’t know the band.
Not their faces.
Not their story.

But the words fit.

Like makeup stretched over my body.

\vspace{0.618cm}

Modeling was never mine.

\\
It was assigned.

\\
I was always hungry.
\\
Always reaching.

But Mother—
for once—
that was enough.

\vspace{0.618cm}

\dialogue{Photographer}{Turn your head right}
\action{The words landed with the quiet authority of a verdict.}

\vspace{0.618cm}

\dialogue{Mother}{Today’s session was good. Please, smile more. You embarrass me in front of John.}
\action{Her voice carried disapproval, stitched into the low hum of the engine.}

\vspace{0.618cm}

\dialogue{Maga}{Yes, Mom.}
\action{The words left my mouth already hollow, as if language itself had given up on me.}

\vspace{0.618cm}

For as long as I can remember,
modeling had been my life.

\\
Not a choice.

\\
Friends?
I had them.

Faces that smiled wide for cameras.
Voices polished smooth as glass.

But truth?

\\
Truth doesn’t last long
in a world where reflection matters
more than reality.

\vspace{0.618cm}

\dialogue{Maga}{Yes, Mom.}
\action{The phrase released again, untethered from meaning.}

\vspace{0.618cm}

Boyfriends?
Sure.

They loved the skin.
The smile.
The body shaped by a thousand flashes.

\\
Not me.

\\
Sometimes I caught my reflection—
really looked—
and wondered who that stranger was,
trapped behind glass.

\vspace{0.618cm}

\dialogue{Maga}{Yes, Mom.}
\action{Barely a breath now. A thread unraveling.}

\vspace{0.618cm}

Her phone rang.

Sharp.
Shrill.

It cut through the silence like a blade.

\\
Father.

\\
The only person who had ever truly loved me.
And even that hadn’t been enough.
Not against her gravity.

\vspace{0.618cm}

They were fighting again.
Of course they were.

\\
Years of it.
The same war,
replayed.

\\
I was almost nineteen.
Old enough to see the cracks
were not cracks anymore—
they were fault lines.

\\
This time, I thought,
it might finally be over.

\vspace{0.618cm}

\dialogue{Mother}{You—WHAT? Daniel, what are you saying? Divorce? NO. Daniel. I won’t talk about this. This is bullshit.}
\action{Her words came out sharp, furious, even as she already knew the war was lost.}

\vspace{0.618cm}

The call ended.

She stared at the road ahead.

Then snapped.

Words flew—
senseless,
cutting,
like broken glass.

\\
He had done it.
He had left.

\\
A strange pride bloomed inside me.
At least one of us had escaped.

\vspace{0.618cm}

Mother was never a good driver.

\\
A cliché, really.

\\
And the rage twisting through her
wasn’t helping.

\vspace{0.618cm}

The world lurched.

\\
Shifted.

\\
I blinked.

The ringing in my ears
was alive.

\vspace{0.618cm}

The car stopped—
but not because we chose it to.

Twisted metal.
Silence.

I turned my head.

Blood.

\vspace{0.618cm}

And for the first time in my life,
I saw her cry.

\vspace{0.618cm}

\dialogue{Mother}{Did you know your grandma was never satisfied with my life decisions? Everything I did was never enough for her?}
\action{Her words slipped out between ragged breaths, caught between pain and release.}

\dialogue{Mother}{I hated her all my life.}
\action{The sentence carried the fragile weight of something final.}

\vspace{0.618cm}

I remembered.

\\
No one had ever been enough for Grandma.
\\
Not for her.
\\
Not for anyone.

\vspace{0.618cm}

I looked around.
The wreckage.
The bent metal.
The bleeding woman beside me.

\\
We would survive this.

Somehow.

\vspace{0.618cm}

But as I looked at my mother—
small,
broken,
reduced to something I had never seen before—

a thought formed,
clear and steady,
inside my bruised mind.

\\
The cycle has to end.

\\
And it will end with me.

\vspace{0.618cm}

\dialogue{Mother}{Would you forgive me?}
\action{She cried, exposed, unguarded.}

\vspace{1cm}

\dialogue{Maga}{You have done nothing wrong, Mom.}
\action{My voice was soft. Calm. Carrying the weight of truth—and the quiet mercy of forgiveness.}

% === Story 4 ===
\chapter*{Her Wedding}
\addcontentsline{toc}{chapter}{Her Wedding}

\dialogue{Maga}{You’re going to make this about yourself, Mom, right?}
\action{She meant to keep the thought caged.
It slipped out anyway.}

\dialogue{Fiancé}{Pardon me, love?}
\action{His voice hovered between confusion and concern.}

\dialogue{Maga}{Oh—sorry.
I thought I was still in my head.}
\action{She gathered herself carefully.}

\dialogue{Fiancé}{Yeah, but… what was that?}
\action{Still searching.}

\dialogue{Maga}{You know.
My mom is going to make my wedding about her.}
\action{A soft surrender.}

\dialogue{Fiancé}{Ah, love…
I’m sure she means well.}
\action{He said it gently,
as if he had already learned how to live beside the truth.}

\dialogue{Maga}{How do you do it?}
\action{The question carried admiration—and envy.}

\dialogue{Fiancé}{Do what?}

\dialogue{Maga}{How do you always see the good in people?}
\action{Half a question.
Half a confession.}

\dialogue{Fiancé}{I don’t know.
Things are complicated, I guess.}
\action{He sounded unsure even of himself.}

\dialogue{Fiancé}{It’s hard for me to believe in evil.}
\action{A small smile.
Unarmored.}

\vspace{0.618cm}

\dialogue{Wedding Planner}{There you are!
Your mother is looking for you everywhere.}
\action{Barely holding it together.}

\dialogue{Maga}{Here.
We.
Go.}
\action{She felt the weight settle on her shoulders.}

\vspace{0.618cm}

\dialogue{Mother}{Why aren’t the Johnsons at table nine?}
\action{Judgment sharpened into command.}

\dialogue{Wedding Planner}{Because—}
\action{She barely began.}

\dialogue{Mother}{Doesn’t matter.
Make it happen.}

\dialogue{Mother}{And while you’re at it,
I need to move two tables.
The Wayans and the Jeffersons are very important.
Influential families.}

\dialogue{Mother}{Why are you so calm?}

\dialogue{Mother}{Sigh.
Never mind.}

\vspace{0.618cm}

\dialogue{Mother}{I can’t believe how much work I had to do
to make this wedding even happen.}
\action{Her voice slipped easily into monologue.}

\dialogue{Maga}{Shut up.}
\action{Thought.}

\dialogue{Mother}{Honestly,
if it weren’t for me,
there wouldn’t be a wedding worth attending.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{I picked the venue.
I chose the menu.
Let’s be honest—my daughter has no real taste.
And don’t get me started on the guest list.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{My friends deserved to be here.
Half these people came because of me.
Not her.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{Everyone kept telling me
how stunning everything looked,
how beautiful the arrangements were,
how they could feel the love—
as if I hadn’t orchestrated every detail.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{I basically saved her from embarrassment.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{Her dress?
My choice.
Her makeup?
Thank God I intervened.
She would’ve looked like a washed-out little girl without me.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{When she walked down the aisle,
all I could think was:
Look at what I created.
Look at the masterpiece I made.

This day—
let’s be honest—
is as much about me as it is about her.
Maybe more.

It’s my legacy walking down that aisle.
Everyone saw it.
Everyone knew it.
They were applauding me too—
whether they admitted it or not.}
\action{The air felt thin.
Like it might finally run out.}

\dialogue{Maga}{Shut up.}

\dialogue{Mother}{Oh dear Lord in Heaven!
Damian—that tie, no!}
\action{She shouted.}

\vspace{0.618cm}

\dialogue{Maga}{No.
Shut up.
SHUT UP.
SHUT THE FUCK UP, MOM!}
\action{The storm broke.
There was no holding it anymore.}

\dialogue{Maga}{This is my goddamn wedding.
This is my fucking husband.
Get it through your head!}

\vspace{0.618cm}

\dialogue{Mother}{Sigh.
Whatever.
I have other important things to attend to.}
\action{Dismissive.
Unmoved.}

\vspace{0.618cm}

\dialogue{Maga}{\ldots}
\action{She swallowed what was left.
Some battles are lost before they’re spoken.}

\vspace{0.618cm}

\dialogue{Fiancé}{Come here, love.}
\action{Steady.
Present.}

\dialogue{Maga}{I love you, Damian.
I really do.}
\action{She said it like a prayer—
not asking,
but anchoring.}

% === Story 5 ===
\chapter*{Oh Sweety, That's Wrong}
\addcontentsline{toc}{chapter}{Oh Sweety, That's Wrong}

The old lady reached into her bag and finally found what she was looking for.

A piece of candy.

She unwrapped it slowly, deliberately, as if the act itself mattered.

\dialogue{Old Lady}{Here.}{said simply}

Maga accepted it, surprised by the tenderness of the gesture. It tasted like childhood. Sugar and time.

\dialogue{Old Lady}{You see, Sweety…}{paused, choosing her words with care}
\dialogue{Old Lady}{Sometimes the question isn’t why you don’t want what others want.}{...}
\dialogue{Old Lady}{Sometimes the question is who taught you what wanting looks like.}{...}

Maga felt something shift—not click, not resolve—just tilt.

The old lady leaned back against the bench, eyes following a child chasing pigeons across the grass.

\dialogue{Old Lady}{We don’t grow up free.}{said quietly}
\dialogue{Old Lady}{We grow up trained.}{...}

Maga swallowed.

\dialogue{Old Lady}{Love, ambition, desire… they don’t arrive unfiltered.}{...}
\dialogue{Old Lady}{They pass through hands first.}{...}
\dialogue{Old Lady}{And some hands…}{paused}
\dialogue{Old Lady}{hold too tight.}{...}

The words didn’t accuse.

They didn’t absolve.

They simply *were*.

Maga stared ahead, watching a couple argue softly near the fountain. The woman gestured wildly. The man folded into himself.

\dialogue{Maga}{So what if I don’t know what I want?}{asked}
\dialogue{Maga}{What if I never do?}{...}

The old lady smiled—not sadly, not kindly—but knowingly.

\dialogue{Old Lady}{Then maybe wanting isn’t your work.}{...}
\dialogue{Old Lady}{Maybe listening is.}{...}

A breeze passed through the park, scattering leaves, lifting hair, erasing the outlines of the moment.

Maga blinked.

The bench beside her was empty.

No old lady.

No candy wrapper.

Only the faint warmth where someone had been sitting.

She looked down at her hands.

The candy was gone.

Had it ever been there?

Children still laughed. Lovers still clung. The world resumed its careless choreography.

But something lingered.

Not an answer.

A permission.

Maga stood, brushing invisible crumbs from her palms.

As she walked away, one thought followed her—not loud, not demanding—but persistent enough to matter:

\textit{What if nothing is wrong with me?}

And somewhere, beneath that thought, quieter still:

\textit{What if it never was?}

% === Story 6 ===
\chapter*{A Cigarette After Sex}
\addcontentsline{toc}{chapter}{A Cigarette After Sex}

The man didn’t answer right away.

He inhaled—not theatrically, not as a performance—but as if he needed air before truth. His eyes never left the canvas.

\dialogue{Man in the back}{It feels like the moment after pretending you’re fine}{said at last}
\dialogue{Man in the back}{When no one’s watching anymore}{...}

Something in Maga tightened.

Not pain. Recognition.

\dialogue{Maga}{Yes}{answered too quickly}

Silence settled between them, not awkward, not empty. The kind that only exists when two people stand at the same edge without needing to name it.

Around them, laughter bloomed and burst. Glasses clinked. Applause erupted somewhere near the front of the gallery. Someone was congratulating someone else for being seen.

The man finally turned to her.

He wasn’t remarkable. Not handsome in the way magazines trained people to notice. Not impressive. Just… present. As if he hadn’t arrived to be validated.

\dialogue{Man in the back}{It doesn’t ask for sympathy}{continued}
\dialogue{Man in the back}{That’s what makes it uncomfortable}{...}
\dialogue{Man in the back}{It doesn’t beg to be saved}{...}

Maga let out a breath she hadn’t known she was holding.

\dialogue{Maga}{I didn’t want it to be forgiven}{said}
\dialogue{Maga}{I wanted it to be honest}{...}

He nodded.

Once.

A small gesture, but it carried weight.

\dialogue{Man in the back}{Most people want art to absolve them}{...}
\dialogue{Man in the back}{This one doesn’t}{...}

They stood there a moment longer, side by side, watching the painted smoke curl upward into nothing.

Then the man stepped back.

\dialogue{Man in the back}{Thank you}{said simply}

No exchange of names.

No promise.

No attempt to turn the moment into something it wasn’t.

He disappeared into the crowd, absorbed by the noise, leaving behind only the echo of being understood without being claimed.

Maga stayed where she was.

For the first time that night, she didn’t feel invisible.

Nor exposed.

Just… intact.

Later, when the gallery emptied and the lights dimmed, she stepped outside alone. The night air was cool, forgiving. The city hummed with lives intersecting and diverging without ceremony.

She leaned against the brick wall and reached into her coat pocket.

A cigarette.

She turned it between her fingers, feeling its fragility. The promise. The lie.

Maga smiled.

And then—

She put it back.

Not because she was healed.

Not because she was stronger.

But because, tonight, she didn’t need to prove she existed by burning.

She walked home with the quiet certainty that some acts of survival don’t look like victory.

They look like restraint.

And sometimes, that’s enough.

% === Story 7 ===
\chapter*{The Guru}
\addcontentsline{toc}{chapter}{The Guru}
Maga felt something loosen.

Not relief.  
Not peace.  

Permission.

\vspace{0.618cm}

She had spent her life choosing.  
Or believing she was.

Choosing survival.  
Choosing silence.  
Choosing the least dangerous exit in a room full of knives.

Every choice had cost her something.  
Every decision carved away a little more skin.

\vspace{0.618cm}

\dialogue{Maga}{But if I don’t choose…}{her voice barely existed}
\dialogue{Maga}{If I don’t run, don’t fight, don’t submit… what happens to me?}{...}

The Guru smiled—not kindly, not cruelly. Precisely.

\dialogue{The Guru}{Then you discover who remains when fear no longer negotiates on your behalf}{said}

\vspace{0.618cm}

The words landed softly, like ash.  
They did not burn.

\vspace{0.618cm}

That night, she dreamed.

No monsters.  
No memories.  

Only rain.

\vspace{0.618cm}

She stood naked beneath it, not ashamed, not exposed. The water struck her skin without judgment. Each drop erased a demand. A name. A role she had been forced to play.

She did not ask the rain to stop.  
She did not ask it to stay.

She let it be.

\vspace{0.618cm}

In the morning, something had shifted.

Not healed.  
Not resolved.

But quieter.

\vspace{0.618cm}

The retreat ended. As retreats always do. People hugged. Exchanged promises they would forget. Packed enlightenment into suitcases too small to hold it.

Maga left without ceremony.

\vspace{0.618cm}

She did not become holy.  
She did not become pure.  
She did not forgive the world.

\vspace{0.618cm}

But she stopped searching for shelter in the wrong places.

Not in bodies.  
Not in titles.  
Not in being wanted.

\vspace{0.618cm}

For the first time, she understood something simple and terrifying:

She had survived not because she was broken,  
but because she had adapted to an impossible terrain.

\vspace{0.618cm}

And adaptation, she realized, is not weakness.

It is intelligence under siege.

\vspace{0.618cm}

Maga walked back into her life without answers, without vows, without illusions.

But now, when the storm came—and it still did—  
she no longer mistook endurance for love.

She stood.

She breathed.

And sometimes, just sometimes,

she let the rain touch her without asking it to mean anything at all.


% === Epilogue ===
\chapter*{Epilogue}
\addcontentsline{toc}{chapter}{Epilogue}

I don’t say that to diminish it.

On the contrary.

\vspace{0.618cm}

If nothing were fleeting, nothing would matter. If every wound healed by default, there would be no courage in bleeding. If every goodbye were reversible, no hello would ever feel brave.

\vspace{0.618cm}

Mortality is not the flaw in the design.

It is the design.

\vspace{0.618cm}

I have watched beings curse their last breath and beg for more time. I have watched others walk toward death with a calm so complete it frightened even me. The difference was never strength. Never wisdom.

It was meaning.

\vspace{0.618cm}

Those who lived as if time mattered did not fear its end.

Those who wasted it demanded eternity as compensation.

\vspace{0.618cm}

I have been both.

\vspace{0.618cm}

There were eras when I hid from loss, when I believed detachment was enlightenment. I told myself I was above longing, above grief, above the smallness of human ache.

I was wrong.

\vspace{0.618cm}

Detachment is not transcendence.

It is anesthesia.

\vspace{0.618cm}

You numb yourself long enough and even wonder disappears. You stop asking questions not because you found answers, but because nothing surprises you anymore.

That is the true death.

\vspace{0.618cm}

So if you are reading this from within the brief flicker of a human life, listen carefully:

\vspace{0.618cm}

Do not envy the immortal.

Do not pray for endless time.

Do not curse the fragility of your days.

\vspace{0.618cm}

Your fear is the proof that something matters.

Your grief is the echo of love having existed.

Your anger means you still believe the world can be better.

\vspace{0.618cm}

Even your mistakes are holy.

They mean you were present when the choice was made.

\vspace{0.618cm}

I would trade centuries for one unrepeatable moment.

One imperfect decision.

One love that does not last long enough.

\vspace{0.618cm}

Because eternity explains everything.

And explanation is the enemy of wonder.

\vspace{0.618cm}

So go.

Live quickly.

Live clumsily.

Forgive badly.

Love without guarantees.

\vspace{0.618cm}

And when the end comes—and it will—do not greet it as a thief.

Greet it as the quiet proof that your life was finite enough to matter.

\vspace{1cm}

\begin{quote}
\centering
\textit{Nothing eternal can teach you this.
\\
Only something that ends.}
\end{quote}

\end{document}
